R Notebook

### 2020-02-03 src/testing_file.Rmd
dong barbaric things to remi's code

```{r}
streams <- raster::shapefile("../data/env/landp/land-wgs84v2.shp")
ras <-

ggplot() + layer_spatial(data = streams, fill = "dark grey", colour = "transparent") + layer_spatial() + theme_void()

@@

>>>>

@@

now create a table to see how many cells there are >0.5 in each month

```{r count cells >0.5}

binaryprob_list <- list.files("../output/maxent/paper_plots/hotspot_mapping", pattern = ".*_bin_0.5_2d.asc", full.names = TRUE)
sum2d <- data.frame(matrix(ncol = 2, nrow = 10))
sum2d <- setNames(sum2d, c("month", "count"))

#get proportion
tcs <- read.csv("../output/maxent/paper_plots/cellsperlayer.csv", header = TRUE) #file showing how many cells per depth
#tcs <- tcs[-c(1:3), ] #because the top three rows are deeper than the capelin obs...
totc <- sum(tcs$no_cells)

#2-d map edited for value as remi cunted of the cells in the layer i sent and not with all the layers.

#quickest way might be just to inject my csv file with the correct values here....
df2 <- read.csv("../output/maxent/paper_plots/cell_count_0.5.csv", header = TRUE)
df$total <- df2$proportion
df$total <- format(round(df$total, digits = 2))
#colnames(df) <- c("month", "cellc", "total")
